The dark side of big data

### 2021-11-19 text/21/dark-side.Rmd
Moved notes pages back on dark-side.Rmd
Started work on nhanes-overview.md

---
title: "The dark side of big data"
source: "New"
date: "2021-10-28"
categories:
- Blog post
tags:
- Big data
- Incomplete page
output: powerpoint_presentation
---

@@

>>>>

---
title: "The dark side of big data"
source: "New"
date: "2021-10-28"
categories:
- Blog post
tags:
- Big data
- Incomplete page
output: html_document
---

@@

On the next couple of slides, I want to show a classic Venn diagram and my variation on it to illustrate an important point.
